---
title: Differences across HFE genotypes in serum iron parameters at genotyping
author: Lorenz M. Pammer, MD
date: last-modified
editor: source
page-layout: full
format:
  eisvogel-pdf:
    default:
      fig-align: center
      fig-width: 10
      fig-asp: 0.618
      fig-dpi: 300
      papersize: a4
      layout: constrained
      geometry:
        - top=30mm
        - bottom=30mm
        - heightrounded
      mainfont: Source Sans Pro
      sansfont: Source Sans Pro
      fig-responsive: false
  html:
    figure-width: 100%
    fig-align: center
    default-image-extension: svg
execute:
  echo: false
  warning: false
  #bibliography:
---


```{r}
library(here)
library(gtsummary)
library(tidyverse)
library(showtext)
library(kableExtra)
load(here::here("./data/workspaces/processed/for_qmd/","file.RData"))
showtext_auto()


```

# Tables

## Table 1
@tbl-baseline1 shows the baseline characteristics of the study population, stratified by HFE genotype.

```{r}
#| label: tbl-baseline1
#| fig-cap: "Table 1 - baseline statistics"
tbl_sum1 %>% 
  modify_table_body(
    ~ .x %>% mutate(across(where(is.character), ~ gsub("N=", "\nN=",.)))
                           )%>%
  modify_header(all_stat_cols() ~"**{level}**, \n N = {n}")   -> tbl1
  
tbl1 %>% as_flex_table() %>% flextable::set_table_properties(., layout = "autofit")
```

\newpage

# Figures
## Figure 1
@fig-num1 shows the different distributions of ferritin across genotypes.

```{r}
#| label: fig-num1
#| fig-cap: "Ferritin between genotypes, split by sex "
#| fig-width: 5
#| fig-height: 6
# ggplot_ob

``` 
\newpage
## Figure 2
@fig-num2 shows the different distributions of log10(ferritin) across genotypes.
```{r}
#| label: fig-num2
#| fig-cap: "Log10(ferritin) between genotypes, split by sex "
#| fig-width: 5
#| fig-height: 6
# ggplot_ob
``` 
\newpage
## Figure 3
@fig-num3 shows the different distributions of TSAT across genotypes.
```{r }
#| label: fig-num3
#| fig-cap: "TSAT between genotypes, split by sex "
#| fig-width: 5
#| fig-height: 6
# ggplot_ob
``` 
\newpage
## Figure 4
@fig-num4 shows the different distributions of serum iron across genotypes.
```{r }
#| label: fig-num4
#| fig-cap: "Serum iron between genotypes, split by sex "
#| fig-width: 5
#| fig-height: 6
# ggplot_ob
``` 